Using Fundamental Measure Theory to treat the Pair Distribution Function of the Inhomogeneous Hard-Sphere Fluid

### 2013-08-21 papers/pair-correlation/paper.tex

\newcommand{\fixme}[1]{\red{[#1]}}

@@

>>>>

\newcommand{\fixme}[1]{\text{\red{[#1]}}}

@@

We here construct a separable fit to the radial distribution function
$g(r, g_\sigma)$, which is a function of the radius $r$ and its value
at contact $g_\sigma$.  We could convert this to a more conventional
function of the packing fraction $\eta$ by inverting the
Carnahan-Starling formula for $g_\sigma$
\begin{equation}
  g_\sigma = \frac{1-\tfrac{\eta}{2}}{(1-\eta)^3}
\end{equation}
but that would add an unnecessary step in the use of $g(r)$, since the
averaged value of $g_\sigma$ is what we can directly compute for the
inhomogeneous system.

We construct $g(r, g_\sigma)$ using several constraints.  Naturally,
\begin{equation}
  g(\sigma, g_\sigma) = g_\sigma.
\end{equation}
In addition, we know that
\begin{equation}
  \begin{split}
  \int (g(r)-1)d\rr &= \frac{\chi_T}{kT} \\
  &= \eta \eta \cdots \fixme{fill in, double-check}
  \end{split}
\end{equation}
where $\chi_T$ is the isothermal compressibility, for which we use the
Carnahan-Starling equation of state.

An additional constraint that we use sets the slope of $g(r,
g_\sigma)$ at $r=\sigma$.  \fixme{explain this}

Given these constraints, we use a functional form of
\begin{equation}
  g(r,g_\sigma) = 1 + A e^{-a(r-\sigma)}
  + B (r-\sigma) e^{-b(r-\sigma)} + C (r-\sigma)^2 e^{-c(r-\sigma)}
\end{equation}
where $A$, $B$, and $C$ are amplitudes determined by the above
constraints, and $a$, $b$, and $c$ are parameters fit to Monte Carlo
simulations of the hard-sphere radial distribution function.

\fixme{add paragraphs and equations with $A$, $B$ and $C$}

\fixme{add table with parameters}
